Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model

### 2014-03-10 Paper/gammaRays.tex
Added / Redesigned some plots

In this paper we consider all the bursts observed by Fermi-LAT since 2008 August 4 to 2011 August 1, for which at least $10$ events with energies $\unit[1]{GeV}$ or higher were observed. There are $3$ of them: GRB080916C, GRB090902B, and GRB090926A. We study their light curves in two bands, $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$.
The Kolmogorov-Smirnov test is used to check whether the light curves for these two bands are the same. No significant difference was found for GRB080916C and GRB090902B. However, we observed with statistical significance of $3.4 \sigma$, that the higher energy light curve of GRB090926A is stretched with respect to the lower-energy one.

@@

@@

\begin{figure}[kappaDistribution]
        \centering
        \begin{subfigure}[kappaDistributionHistogram]{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionHistogram}
                \label{fig:kappaDistributionHistogram}
        \end{subfigure}
        \begin{subfigure}[kappaDistributionCDF]{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionCDF}
                \label{fig:kappaDistributionCDF}
        \end{subfigure}
        \caption{The histogram and the CDF of the stretching factors sample produced by our model (blue). The sample contains $600$ points. The red curve is an empirical CDF of the observed sample (3 points).}
        \label{fig:kappaDistribution}
\end{figure}

>>>>

In this paper we consider all the bursts observed by Fermi-LAT since 2008 August 4 to 2011 August 1, for which at least $10$ events with energies $\unit[1]{GeV}$ or higher were observed. There are $4$ of them: 080916C, 090510, 090902B, and 090926A. We study their light curves in two bands, $(\unit[100]{MeV}, \unit[1]{GeV})$ and $(\unit[1]{GeV}, \unit[300]{GeV})$.
The Kolmogorov-Smirnov test is used to check whether the light curves for these two bands are the same. No significant difference was found for 080916C and 090510. However, we observed with statistical significance of $3.3 \sigma$, that the higher energy light curve of 090926A is stretched with respect to the lower-energy one, and with statistical significance of $2.2 \sigma$, that the lower energy light curve of 090902B is stretched with respect to the higher-energy one.

@@

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve080916C}
                \label{fig:lightCurve080916C}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities080916C}
                \label{fig:probabilities080916C}
        \end{subfigure}
        \caption{080916C}
        \label{fig:grb080916C}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090510}
                \label{fig:lightCurve090510}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090510}
                \label{fig:probabilities090510}
        \end{subfigure}
        \caption{090510}
        \label{fig:grb090510}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090902B}
                \label{fig:lightCurve090902B}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090902B}
                \label{fig:probabilities090902B}
        \end{subfigure}
        \caption{090902B}
        \label{fig:grb090902B}
\end{figure}

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{lightCurve090926A}
                \label{fig:lightCurve090926A}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{probabilities090926A}
                \label{fig:probabilities090926A}
        \end{subfigure}
        \caption{090926A}
        \label{fig:grb090926A}
\end{figure}

@@

\begin{figure}
        \centering
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionHistogram}
                \label{fig:kappaDistributionHistogram}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
                \includegraphics[width=\textwidth]{kappaDistributionCDF}
                \label{fig:kappaDistributionCDF}
        \end{subfigure}
        \caption{The histogram and the CDF of the stretching factors sample produced by our model (blue). The sample contains $600$ points. The gray curve is an empirical CDF of the observed sample (4 points).}
        \label{fig:kappaDistribution}
\end{figure}
